---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
#1.Loading the data 
```{r}
library("data.table")
activityDT <- data.table::fread(input = "activity.csv")


## What is mean total number of steps taken per day?
#1.Calculate the total number of steps taken per day
```{r}
Total_Steps <- activityDT[, c(lapply(.SD, sum, na.rm = FALSE)), .SDcols = c("steps"), by = .(date)] 

head(Total_Steps, 10)
 ##        date steps
 ##1: 2012-10-01    NA
 ##2: 2012-10-02   126
 ##3: 2012-10-03 11352
 ##4: 2012-10-04 12116
 ##5: 2012-10-05 13294
 ##6: 2012-10-06 15420
 ##7: 2012-10-07 11015
 ##8: 2012-10-08    NA
 ##9: 2012-10-09 12811
##10: 2012-10-10  9900

#2.If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day

#3,Calculate and report the mean and median of the total number of steps taken per day


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
